---
title: "Consumer Complaints"
author: "Jack Wild"
date: "4/18/2022"
output: html_document
---
First I loaded all my packages in, as well as the dataset. 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) #includes ggplot2
library(janitor) 
library(scales)
library(lubridate)
library(ggthemes)
library(dplyr)

complaints <- read_rds("complaints.rds")

head(complaints)

```

Next, I first did a count to see which type of product received the most complaints. I then found that subproduct was more digestible. 

```{r}

complaints %>% count(product, sort = TRUE)

complaints %>% count(sub_product, sort = TRUE)

```

Next, I did a count to see which company had the most complaints filed against them. 

```{r}

complaints %>% count(company, sort = TRUE)

```
Then I decided to take a look at the companies that lack timely responses, as if I were a consumer, I would want to know that information. 

```{r}

complaints %>% filter(timely_response == "No") %>% 
  count(company, sort = TRUE)


complaints_responses <- head(complaints %>% filter(timely_response == "No") %>% 
  count(company, sort = TRUE))

complaints_responses

```
Next, I did a count to see where the most complaints come from. It would be interesting to compare these numbers to the relative population. 

```{r}

complaints %>% 
  count(state, sort = TRUE)


complaints_states <- head(complaints %>% count(state, sort = TRUE))

complaints_states

ggplot(complaints_states , aes(x=state , y=n, width=.25)) + geom_bar(stat="identity", color="#9ebcda", fill= "#9ebcda") +
  scale_y_discrete(name="Testing") +
  scale_x_discrete(name="Testing 2") +
  labs(title = "Testing Title", 
       caption = "By Jack Wild") +
  geom_text(stat="identity", label=complaints_states$n, vjust= 1, size=3)



```

Then, I tried to make a chart to show how the number of complaints has changed over time. Unfortunately it didn't look to great and I was haviong trouble changing the date labels so I decided not to include this on my flexdashboard. 

```{r}

complaints_year <- complaints %>% count(mm_yy_received, sort = TRUE)

complaints_year

ggplot(complaints_year , aes(x=mm_yy_received , y=n, width=.25)) +
  geom_bar(stat="identity", color="#9ebcda", fill= "#9ebcda") +
  scale_y_discrete(name="Testing") +
  scale_x_discrete(name="Testing 2") +
  labs(title = "Testing Title", 
       caption = "By Jack Wild") +
  geom_text(stat="identity", label=complaints_year$n, vjust= .5, size=.5)

```
